Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recognition

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
typos, todos

\title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recognition}

@@

Most successful neural approaches also model some notion of context.
We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018}.
Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.

@@

@@

\citet{petersTuneNotTune2019} investigate when it is best to fine-tune BERT for sentence classification tasks.
They find that when the target task is very similar to the pre-training task, fine-tuning provides less of a performance boost.
We note that there is some conceptual relationship between DAR and next sentence prediction, since the a dialogue act constrains (or at least is predictive of) the dialogue act that follows it.

@@

Although our experiments with further pre-training were inconclusive, \citet{baoPLATOPretrainedDialogue2019} finds that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection.
Further pre-training may be helpful for DAR too, if the in-domain or cross-domain corpus is large enough.
It remains an open question, however, how well the text chat and social media domains transfer to transcribed dialogue

>>>>

\title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recognition}
% TODO rename

@@

Most successful neural approaches also model some notion of context.
We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018}.
Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.
% TODO: RNN with attention:
% - Conversational Analysis using Utterance-level Attention-based Bidirectional Recurrent Neural Networks (Bothe et al., Interspeech 2018)
% - A Unified Neural Architecture for Joint Dialog Act Segmentation and Recognition in Spoken Dialog System (Zhao and Kawahara, SIGdial 2018)

% TODO DAR not for

@@

% TODO: more refs
% Chakravarty et al., "Dialog Acts Classification for Question-Answer Corpora," ASAIL 2019.
% - Ribeiro et al., "Deep Dialog Act Recognition using Multiple Token, Segment, and Context Information Representations," Journal of Artificial Intelligence Research, 2019
% - Yu et al., "MIDAS, A Dialog Act Annotation Scheme for Open-Domain Human-Machine Spoken Conversations," arxiv 2019.

@@

\citet{petersTuneNotTune2019} investigate when it is best to fine-tune BERT for sentence classification tasks.
They find that when the target task is very similar to the pre-training task, fine-tuning provides less of a performance boost.
We note that there is some conceptual relationship between DAR and next sentence prediction, since the dialogue act constrains (or at least is predictive of) the dialogue act that follows it.

@@

Although our experiments with further pre-training were inconclusive, \citet{baoPLATOPretrainedDialogue2019} finds that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection.
Further pre-training may be helpful for DAR too, if the in-domain or cross-domain corpus is large enough.
It remains an open question, however, how well the text chat and social media domains transfer to transcribed dialogue.
